*Prochlorococcus marinus* responses to light and oxygen

### 2024-06-06 Code/Manuscript_O2.Rmd
minor edits
caption for map figure

XXXX
The potential for niche expansion into temperate regions by *P. marinus*
varies depending on the season, which influences achieved underwater
photoperiods and light levels. Temperate summer delivers ~11 hours of
blue waveband light underwater, above the photic threshold of 20 µmol
photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of
blue waveband light underwater, photoperiod ranges which are permissive
for growth of all three *P. marinus*. In contrast temperate winter
delivers only about 2 h of blue waveband light underwater above the
photic threshold, which precludes growth of MED4 and SS120, even if
winter waters reached permissive temperatures. MIT9313 and SS120 will be
excluded from near-surface growth niches by high PAR, unless OMZ zones
extend to the near surface (Table \@ref(tab:NichesTable).

@@

NichesMap_cap <- glue(" Figure caption for Potential Temperate Future Niche map goes here.",

>>>>

XXXXDoug
The potential for niche expansion into temperate regions by *P. marinus*
varies depending on the season, which influences achieved underwater
photoperiods and light levels. Temperate summer delivers ~11 hours of
blue waveband light underwater, above the photic threshold of 20 µmol
photons m^-2^ s^-1^, while temperate spring/fall delivers 8 hours of
blue waveband light underwater, photoperiod ranges which are permissive
for growth of all three *P. marinus*. In contrast temperate winter
delivers only about 2 h of blue waveband light underwater above the
photic threshold, which precludes growth of MED4 and SS120, even if
winter waters reached permissive temperatures. MIT9313 and SS120 will be
excluded from near-surface growth niches by high PAR, unless OMZ zones
extend to the near surface (Table \@ref(tab:NichesTable).

@@

NichesMap_cap <- glue(" Potential Future Niches for *Prochlorococcus* clades in a warming ocean. 
The map shows current latitudinal distribution limits for *Prochlorococcus* (between green dashed lines), tropical and temperate  latitudinal regions (yellow bands). 
Light levels, photoperiods and spectral bands, potentially permissive for growth of *Prochlorococcus* clades are determined by the interactions of latitude, season and depth attenuation of light.
Potential clade occupancies under Full Oxygen (250 µM O~2~) are shown for 10-50 m and 100 m depths, in temperate vs. tropical regions, under depth-resolved photoperiods, approximating Winter Solstice, Equinox and Summer Solstice. Clade HLI is excluded from temperate depths by short photoperiods at Winter Solstice. Clades LLII/III are excluded from shallow depths by excessive light.
Low Oxygen Zones (25 µM O~2~) drastically alter these potential occupancy patterns by excluding Clade HLI from the temperate winter solstice at all depths, and by expanding the exploitation of higher light by Clade LLIV.
Potential clade occupancies for the southern temperate zone mirror the northern temperate zone occupancies.",
                       .sep = " ")
